%# -*- coding:utf-8 -*-
%!TEX root = ../thesis.tex
%%==================================================
%% pub.tex for SJTUThesis
%% Encoding: UTF-8
%%==================================================

\begin{publications}{99}
%    \item\textsc{Chen H, Chan C~T}. {Acoustic cloaking in three dimensions using acoustic metamaterials}[J]. Applied Physics Letters, 2007, 91:183518.
%    \item\textsc{Chen H, Wu B~I, Zhang B}, et al. {Electromagnetic Wave Interactions with a Metamaterial Cloak}[J]. Physical Review Letters, 2007, 99(6):63903.
    
    \item \textsc{Wu N L, Wang X Y, Ge T}, et al. {Parametric identification and structure searching for underwater vehicle model using symbolic regression}[J].  Journal of Marine Science $\&$ Technology, 2017,22(1):51-60. $($SCI$)$
    
    \item \textsc{Wu N L, Wu C, Ge T}, et al. {Pitch Channel Control of a REMUS AUV with Input Saturation and Coupling Disturbances}[J]. Applied Sciences-Basel, 2018, 8(2): 252- 266. $($SCI$)$  

    \item \textsc{Wu N L, Wang M, Ge T}, et al {High-performance maneuvers control for a workclass
	3000m ROV with experiments}[J]. Proceedings of the Institution of Mechanical Engineers, Part I: Journal of Systems and Control Engineering, 2018.$($SCI, under revised$)$
    
    \item 吴乃龙, 吴超, 葛彤, 等. {基于鱼类体线感知机理的水下机器人水流场识别研究}[J]. 机械工程学报, 2016, 52(13):54-59. $($EI$)$
    
    \item \textsc{Wu N L, Wu C, Ge T}, et al. {Underwater vehicle model structure and parameters discovering with genetic programming based
    symbolic regression}[C]. The Twenty-seventh (2017) International Ocean and Polar Engineering Conference. International Society of Offshore and Polar Engineers, 2017. $($EI$)$

    \item \textsc{Wu N L, Ge T, Wu C}, et al. {Water Flow Forecasting of Underwater Vehicle
    based on LDA Compressed Sensing}[C]. The 43 rd Annual Conference of the IEEE Industry Electronics Society(IECON 2017), 2017. $($EI$)$

    \item \textsc{Wu Nai-Long, Liu Zong-Lin, Wu Chao, Ge Tong}, et al. {Robust MRAC with Anti-windup
    Compensator for the Depth Channel of an Autonomous Underwater Vehicle}[C]. International
    Society of Offshore and Polar Engineers, 2018.(EI/ISTP, Accept)


    \item \textsc{Yang R, Clement B, Mansour A, Li M, Wu N-L}. {Modeling of a complex-shaped underwater vehicle for robust control scheme}[J]. Journal of Intelligent $\&$ Robotic Systems,2015, 80(3):491-506.$($SCI$)$    

\end{publications}


